---
title: "Analysis of Mysis relicta occurrence in Lithuania"
author: "Carl Smith, Asta Audzijonyte, Kestutis Arbaciauskas"
date: "2022-09-06"
output: html_document
---
## Libraries

```{r message=FALSE}
#Load libraries
library(tidyverse)
library(lattice)
library(sp)
library(gstat)
library(ggplot2)
library(fields)
library(dplyr)
library(tidyr)
library(performance)
library(see)
library(devtools)
library(outliers)
library(car)
library(effects)
library(lme4)
library(nlme)
library(glmmTMB)
library(lmerTest)
library(MuMIn)
library(performance)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(gridExtra)
library(GGally)
library(plyr)
library(DHARMa)
```

## Read in the data

```{r}
#Import the file into a dataframe

# Import dataframe
mys <- read_csv(file = "mys_clean.csv")
glimpse(mys)

# 'data.frame':	49 obs. of  16 variables:
```

## Data exploration

```{r}
#Any NAs
colSums(is.na(mys))
# No

# OUTLIERS

# Define preferred figure format
My_theme <- theme(axis.text.y = element_blank(),
                  axis.ticks.y = element_blank(),
                  axis.ticks.x=element_blank(),
                  panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))

# A function for dotplots
multi_dotplot <- function(filename, Xvar, Yvar){
  filename %>%
    ggplot(aes(x = {{Xvar}})) +
    geom_point(aes(y = {{Yvar}})) +
    theme_bw() +
    coord_flip() +
    labs(x = "Order of Data")}

#Add ordered observations
mys <- mys %>%
  mutate(order = seq(1:nrow(mys)))

#Select continuous variables to plot
p1 <- multi_dotplot(mys, order, Year)
p2 <- multi_dotplot(mys, order, Rel_mys)
p3 <- multi_dotplot(mys, order, Rel_amp)
p4 <- multi_dotplot(mys, order, PC_mys)
p5 <- multi_dotplot(mys, order, PC_amp)
p6 <- multi_dotplot(mys, order, Area)
p7 <- multi_dotplot(mys, order, Depth_max)
p8 <- multi_dotplot(mys, order, Depth_ave)
p9 <- multi_dotplot(mys, order, Flow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3)

# 1. PC_amp and PC_mys have a lot of zeros
# 2. Area and flow with serious outliers
# 3. Rel_mys could have a problem with zero inflation

# Are data balanced among levels of the categorical covariates?

mys$fLake <- as.factor(mys$Lake_abbr)
table(mys$fLake)
# OK

table(mys$Year)
# Not great

table(mys$Period)
# Good

table(mys$B_mys)
# 0  1 
# 8 41

table(mys$Rel_mys)
# 0  1  2  3 
# 8  8  6 27 

table(mys$PC)
# OK

######################################
#NUMBER OF ZEROS IN THE RESPONSE VARIABLES

# What is the percentage of zeros for response variables?

sum(mys$Rel_mys == 0)
# 8 zeros

######################################

#NORMALITY AND HOMOGENEITY OF DEPENDENT VARIABLE(S)

# Frequency polygon plot - Rel_mys
mys %>% ggplot(aes(Rel_mys)) +
  geom_freqpoly( bins = 3) +
  labs(x = "Relic mysid abundance", y = "Frequency") +
  My_theme +
  theme(panel.border = element_rect(colour = "black", 
                                    fill=NA, size = 1))


#COLLINEARITY
# a summary using the ggpairs command from the GGally library
mys %>% 
  ggpairs(columns = c("Year", "PC_mys", "PC_amp", "PC",
                      "Area", "Depth_max", "Depth_ave", "Flow"), 
          aes(alpha = 0.8), lower = list(combo = wrap("facethist", binwidth = 2))) + 
  My_theme

# PC_mys and PC_amp correlated (use PC instead)
# Average and max depth correlated (use one or the other)

#####################################

#PLOT RELATIONSHIPS

# Plot response variable against covariates
par(mfrow=c(2,3), mar=c(5,5,1,1), cex.lab = 1)
plot(Rel_mys ~ Area,  data = mys,
     xlab = "Area",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_mys ~ Flow,  data = mys,
     xlab = "Flow",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_mys ~ Depth_max,  data = mys,
     xlab = "Max depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_mys ~ Depth_ave,  data = mys,
     xlab = "Ave depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_mys ~ Year,  data = mys,
     xlab = "Year",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

# Any evidence of interactions
ggplot(mys, aes(x = Flow, y = Rel_mys)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(mys, aes(x = Depth_ave, y = Rel_mys)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(mys, aes(x = Depth_max, y = Rel_mys)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)


ggplot(mys, aes(x = Area, y = Rel_mys)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(mys, aes(x = Year, y = Rel_mys)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

# Temporal pattern?
ggplot() +
  geom_point(data = mys, 
                    aes(y = Rel_mys, x = Year),
                    shape = 16, 
                    size = 2)# +
  # facet_wrap( ~ Lake_abbr, scales = "fixed")

# Nothing obvious, except of course that this treats each lake as an independent observation, when we instead have multiple observations in one location

# Check temporal autocorrelation with ACF plot
B0 <- gls(B_mys ~ Year, 
          data = mys,
          na.action = na.omit,
          method = "REML")

par(mfrow = c(1,1), 
    cex.lab = 1.5, 
    mar = c(5,5,2,2), 
    cex.main = 1.5)

E0Full <- rep(NA, nrow(mys))
I      <- is.na(mys$Year) | is.na(mys$B_mys)
E0     <- resid(B0, type = "n")
E0Full[!I] <- E0

acf(E0Full, na.action = na.pass)
# No evidence of autocorrelation based on ACF plot
```

What variables predict presence/abundance of relic mysids?

Data exploration shows:

Outliers in Area and Flow
Zeros in the response variable
Imbalance in Ponto-Caspian mysacean abundance
Collinearity with average and maximum depth, PC amp and mys
No obviously strong interactions
Same sites sampled on multiple occasions (dependency)

Next steps:

1. log transform flow and area
2. Standardize variables for computational efficiency
3. fit GLMM (lake as random intercept)
4. model presence/absence with Bernoulli distribution

## Log transorm and standardise data

```{r}
# 1. log transform flow and area to improve distribution
mys$logArea <- log10(mys$Area)
mys$logFlow <- log10(mys$Flow)

p1 <- multi_dotplot(mys, order, Area)
p2 <- multi_dotplot(mys, order, logArea)
p3 <- multi_dotplot(mys, order, Flow)
p4 <- multi_dotplot(mys, order, logFlow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, nrow = 2)

# Log transformation gives best distribution of these covariates

##############################################

# 2. Standardize variables for computational efficieny
mys$Year.std    <- (mys$Year-mean(mys$Year))/sd(mys$Year)
mys$logFlow.std <- (mys$logFlow-mean(mys$logFlow))/sd(mys$logFlow)
mys$logArea.std <- (mys$logArea-mean(mys$logArea))/sd(mys$logArea)
mys$aDepth.std  <- (mys$Depth_ave-mean(mys$Depth_ave))/sd(mys$Depth_ave)
mys$mDepth.std  <- (mys$Depth_max-mean(mys$Depth_max))/sd(mys$Depth_max)

```

## Find an optimal model

```{r}

# 3. Fit full model
MY1 <- glmmTMB(Rel_mys ~ Period + logFlow.std + logArea.std + aDepth.std + mDepth.std + PC +
                          (1|fLake),
                          compois(link = "log"),
                          data = mys)
drop1(MY1)
# Model:
# Rel_mys ~ Period + logFlow.std + logArea.std + aDepth.std + mDepth.std + 
#     PC + (1 | fLake)
#             Df    AIC
# <none>         159.06
# Period       1 159.99
# logFlow.std  1 163.19
# logArea.std  1 157.73
# aDepth.std   1 157.52
# mDepth.std   1 157.08 <- drop
# PC           1 157.17

#since average and maximum depth are correlated and might inflate variance we fit two alternative models with only average or only maximum depth 
MY1av <- glmmTMB(Rel_mys ~ Period + logFlow.std + logArea.std + aDepth.std + PC +
                          (1|fLake),
                          compois(link = "log"),
                          data = mys)

# Backward model selection
drop1(MY1av)

#             Df    AIC
# <none>         157.08
# Period       1 158.00
# logFlow.std  1 161.32
# logArea.std  1 155.75
# aDepth.std   1 155.94
# PC           1 155.19 <- drop

MY1ma <- glmmTMB(Rel_mys ~ Period + logFlow.std + logArea.std + mDepth.std + PC +
                           (1|fLake),
                           compois(link = "log"),
                           data = mys)

drop1(MY1ma)
# Model:
# Rel_mys ~ Period + logFlow.std + logArea.std + mDepth.std + PC + 
#     (1 | fLake)
#             Df    AIC
# <none>         157.52
# Period       1 159.04
# logFlow.std  1 161.19
# logArea.std  1 155.90
# mDepth.std   1 155.94
# PC           1 155.53 <- drop

##Both maximum and average depth models suggest that presence of PC crustaceans is the first variable to drop. Maximum depth is also the first variable to remove from the full model. So we proceed with the model that contains average depth, area and logFlow, but not Ponto-Caspian crustacean presence

MY1a <- glmmTMB(Rel_mys ~ Period + logFlow.std + logArea.std + aDepth.std +
                           (1|fLake),
                           compois(link = "log"),
                           data = mys)
drop1(MY1a)

#             Df    AIC
# <none>         155.19
# Period       1 158.04
# logFlow.std  1 159.45
# logArea.std  1 153.75 <- drop
# aDepth.std   1 153.94

MY1b <- glmmTMB(Rel_mys ~ Period + logFlow.std + aDepth.std +
                           (1|fLake),
                           compois(link = "log"),
                           data = mys)

drop1(MY1b)

#             Df    AIC
# <none>         153.75
# Period       1 156.62
# logFlow.std  1 158.43
# aDepth.std   1 152.17 <- drop

MY1c <- glmmTMB(Rel_mys ~ Period + logFlow.std +
                           (1|fLake),
                           compois(link = "log"),
                           data = mys)

drop1(MY1c)
#             Df    AIC
# <none>         152.17 <- cannot improve fit by dropping further variables
# Period       1 155.16
# logFlow.std  1 156.43

# Improve fit with different link function?
MY1d <- glmmTMB(Rel_mys ~ Period + logFlow.std +
                          (1|fLake),
                           compois(link = "sqrt"),
                           data = mys)
AIC(MY1c,MY1d)

#       df      AIC
# MY1c  5 152.1734
# MY1d  5 147.0149 <- better fit

# The optimal model is:
MY2 <- glmmTMB(Rel_mys ~ Period + logFlow.std + 
                          (1|fLake),
                           compois(link = "sqrt"),
                           data = mys) 
#comparing to the model with PC
MY2_pc <- glmmTMB(Rel_mys ~ Period + logFlow.std + PC +
                          (1|fLake),
                           compois(link = "sqrt"),
                           data = mys) 
AIC(MY2, MY2_pc)
```


## Explore the optimal model 

```{r}
# Plot the residuals vs fitted values.
par(mfrow = c(1,1), mar = c(5,5,2,2))
E1 <- resid(MY2, type = "pearson")
F1 <- fitted(MY2)
plot(x = F1, 
     y = E1,
     xlab = "Fitted values",
     ylab = "Pearson residuals",
     pch = 16, cex.lab = 1.5)
abline(0, 0, lty = 2)
# OK

# Plot the residuals vs parameters in the model
par(mfrow = c(1,2), mar = c(5,5,2,2))

#Flow
plot(x = mys$logFlow.std, 
     y = E1,
     xlab = "Standardised flow",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

#Period
boxplot(E1 ~ Period, data = mys,
        xlab = "Period",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Variables not in the model
par(mfrow = c(1,3), mar = c(5,5,2,2))

# Plot the residuals vs ave depth
plot(x = mys$aDepth.std, 
     y = E1,
     xlab = "Standardised max depth",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

# Plot the residuals vs area
plot(x = mys$logArea.std, 
     y = E1,
     xlab = "Standardised log area",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# OK

#PC crustaceans
boxplot(E1 ~ PC, data = mys,
        xlab = "PC",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Assess spatial dependency
# Sample-variogram
mydata <- data.frame(E1, mys$Lat, mys$Lon)
coordinates(mydata) <- c("mys.Lat", "mys.Lon")
V1 <- variogram(E1 ~ 1, mydata, cutoff = 2)
plot(V1, pch = 16, col = 1, cex = 1.5,
     xlab = list(label = "Distance", cex = 1.5),
     ylab = list(label = "Semi-variance", cex = 1.5) )
# No obvious trend with distance

```

## Plot model 

```{r}

# Plot fixed effects
set_theme(
  base = theme_bw(),
  axis.textsize = 1)
plot_model(MY2, vline.color = "red", 
           sort.est = FALSE, 
           show.values = TRUE)
# Good

# Random effects
plot_model(MY2, vline.color = "green", type = "re")
# OK

# Model predictions
set_theme(
  axis.ticksize.x = 0.5,
  axis.ticksize.y = 0.5,
  axis.textsize.x = 0.5,
  axis.textsize.y = 0.5,
  axis.linecolor = "black", 
  axis.textcolor = "black",
  axis.tickslen = 0,
  axis.title.size = 0.9,
  axis.title.color = "black",
  axis.textsize = 0.8,
  geom.outline.size = 1,
  legend.pos = "bottom",
  legend.title.face = "italic",
  legend.backgroundcol = "white",
  legend.item.backcol = "white",
  legend.item.bordercol = "white",
  base = theme_blank())

# Define preferred figure format
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))


# Plot model
plot2 <- plot_model(MY2,
                    type = "pred", 
                    terms = c("logFlow.std [all]", "Period"),
                    colors = c("blue", "firebrick2"),
                    show.data = T,
                    pred.type = c("fe"),
                    scale_y_continuous(limits = c(1,3)),
                    title = "",
                    show.legend = F,
                    jitter = 0.2,
                    axis.title = c("",
                                   ""),
                    show.values = F) + My_theme
                    
grid.arrange(plot2, ncol = 2)


# Model summary
summary(MY2)

#              Estimate Std. Error z value Pr(>|z|)    
#(Intercept)   1.50288    0.09530  15.770  < 2e-16 ***
# PeriodP2    -0.28359    0.08921  -3.179  0.00148 ** 
# logFlow.std  0.23142    0.08646   2.677  0.00744 ** 

tab_model(MY2,
          show.zeroinf = F,
          dv.labels = c("Conway-Maxwell Poisson GLMM (relic mysid)"),
          string.pred = "Coefficient",
          string.ci = "Conf. Int (95%)",
          string.p = "P-value",
          p.style = c("numeric"),
          emph.p = FALSE,
          transform = NULL, 
          file = "mysid_model.doc")


```