---
    title: "Analysis of Mysis relicta occurrence in Lithuania"
author: "Carl Smith, Asta Audzijonyte, Kestutis Arbaciauskas"
date: "2022-09-06"
output: html_document
---

## Libraries
    
```{r message=FALSE}
library(tidyverse)
library(lattice)
library(sp)
library(gstat)
library(ggplot2)
library(fields)
library(dplyr)
library(tidyr)
library(performance)
library(see)
library(devtools)
library(outliers)
library(car)
library(effects)
library(lme4)
library(nlme)
library(glmmTMB)
library(lmerTest)
library(MuMIn)
library(performance)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(gridExtra)
library(GGally)
library(plyr)
library(DHARMa)
```

## Read in the data

```{r}
# Import dataframe
amp <- read_csv(file = "amp_clean.csv")
glimpse(amp)

#originally Period 1 and 2 were set to ensure good balance between the data (45 data points in each period). This is now modified to ensure that period 1 and 2 strictly follow years of 20th and 21st centuries, so we are using the column $PeriodStrict instead of $Period. Model selection and results are the same, although the data balance between the two periods is not as good with the strict definition. But the subdivision does not seem as arbitrary. 

amp$Period <- amp$PeriodStrict

## various sensitivity analyses were also conducted, e.g. only with lakes that were sampled in both 20th and 21st centuries. Again, results are the same, so full details are not included. 
# checkedLakes <- unique(amp$Lake_code[which(amp$Period == "P2")])
# checkedLakes <- unique(amp$Lake_code[which(amp$PeriodStrict == "P2")])
# 
# ampFull <- amp
# amp <- ampFull %>% filter (Lake_code %in% checkedLakes)
# # length(unique(amp$Lake_code))
# glimpse(amp)

#three lakes checked with handnet only, for further sensitivity analyses
three_lakes <- c("Gals", "Galv","Vist")


```

## Data exploration

```{r}
#Any NAs
colSums(is.na(amp))
# No

# OUTLIERS

# Define preferred figure format
My_theme <- theme(axis.text.y = element_blank(),
                  axis.ticks.y = element_blank(),
                  axis.ticks.x = element_blank(),
                  panel.background = element_blank(),
           panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                 color = "white", size = 1),
                              text = element_text(size = 14),
                panel.grid.major = element_line(colour = "white", size = 0.1),
                panel.grid.minor = element_line(colour = "white", size = 0.1))

# A function for dotplots
multi_dotplot <- function(filename, Xvar, Yvar){
  filename %>%
    ggplot(aes(x = {{Xvar}})) +
    geom_point(aes(y = {{Yvar}})) +
    theme_bw() +
    coord_flip() +
    labs(x = "Order of Data")}

#Add ordered observations
amp <- amp %>%
  mutate(order = seq(1:nrow(amp)))

#Select continuous variables to plot
p1 <- multi_dotplot(amp, order, Year)
p2 <- multi_dotplot(amp, order, Rel_amp)
p3 <- multi_dotplot(amp, order, Rel_amp)
p4 <- multi_dotplot(amp, order, PC_amp)
p5 <- multi_dotplot(amp, order, PC_amp)
p6 <- multi_dotplot(amp, order, Area)
p7 <- multi_dotplot(amp, order, Depth_max)
p8 <- multi_dotplot(amp, order, Depth_ave)
p9 <- multi_dotplot(amp, order, Flow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3)

# 1. PC_amp and PC_amp have a lot of zeros
# 2. Area and flow with serious outliers
# 3. Rel_amp could have a problem with zero inflation

# Are data balanced among levels of the categorical covariates?

amp$fLake <- as.factor(amp$Lake_abbr)
#ampFull$fLake <- as.factor(ampFull$Lake_abbr)
table(amp$fLake)
# OK

table(amp$Year)
# Not great

table(amp$Period)

table(amp$B_amp)
# 0  1 
# 8 41

table(amp$Rel_amp)
# 0  1  2  3 
# 8  8  6 27 

 # 0  1  2  3 
 # 7 11 25 28 

table(amp$PC)
# OK

######################################
#NUMBER OF ZEROS IN THE RESPONSE VARIABLES

# What is the percentage of zeros for response variables?

sum(amp$Rel_amp == 0)
# 7 zeros

######################################

#NORMALITY AND HOMOGENEITY OF DEPENDENT VARIABLE(S)

# Frequency polygon plot - Rel_amp
amp %>% ggplot(aes(Rel_amp)) +
  geom_freqpoly( bins = 3) +
  labs(x = "Relic ampid abundance", y = "Frequency") +
  My_theme +
  theme(panel.border = element_rect(colour = "black", 
                                    fill=NA, size = 1))


#COLLINEARITY
# a summary using the ggpairs command from the GGally library
# amp %>% 
#   ggpairs(columns = c("Year", "PC_amp", "PC_amp", "PC",
#                       "Area", "Depth_max", "Depth_ave", "Flow"), 
#           aes(alpha = 0.8), lower = list(combo = wrap("facethist", binwidth = 2))) + 
#   My_theme

# PC_amp and PC_amp correlated (use PC instead)
# Average and max depth correlated (use one or the other)

#####################################

#PLOT RELATIONSHIPS

# Plot response variable against covariates
par(mfrow=c(2,3), mar=c(5,5,1,1), cex.lab = 1)
plot(Rel_amp ~ Area,  data = amp,
     xlab = "Area",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Flow,  data = amp,
     xlab = "Flow",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Depth_max,  data = amp,
     xlab = "Max depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Depth_ave,  data = amp,
     xlab = "Ave depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Year,  data = amp,
     xlab = "Year",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

# Any evidence of interactions
ggplot(amp, aes(x = Flow, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Depth_ave, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Depth_max, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)


ggplot(amp, aes(x = Area, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Year, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

# Temporal pattern?
ggplot() +
  geom_point(data = amp, 
                    aes(y = Rel_amp, x = Year),
                    shape = 16, 
                    size = 2)# +
  # facet_wrap( ~ Lake_abbr, scales = "fixed")

# Check temporal autocorrelation with ACF plot
B0 <- gls(Rel_amp ~ Year, 
          data = amp,
          na.action = na.omit,
          method = "REML")

par(mfrow = c(1,1), 
    cex.lab = 1.5, 
    mar = c(5,5,2,2), 
    cex.main = 1.5)

E0Full <- rep(NA, nrow(amp))
I      <- is.na(amp$Year) | is.na(amp$Rel_amp)
E0     <- resid(B0, type = "n")
E0Full[!I] <- E0

acf(E0Full, na.action = na.pass)
# No strong evidence of autocorrelation based on ACF plot

```

 What variables predict presence/abundance of relic amphipods?

 Data exploration shows:

 -Outliers in Area and Flow
 -Zeros in the response variable
 -Imbalance in Ponto-Caspian ampacean abundance
 -Collinearity with average and maximum depth, PC amp and amp
 -No obviously strong interactions
 -Same sites sampled on multiple occasions (dependency)

Next steps:

 1. log transform flow and area
 2. Standardize variables for computational efficiency
 3. fit GLMM (lake as random intercept)
 4. model presence/absence with Bernoulli distribution

## Log transorm and standardise data

```{r}
amp$fLake <- as.factor(amp$Lake_abbr)
# 1. log transform flow and area to improve distribution
amp$logArea <- log10(amp$Area)
amp$logFlow <- log10(amp$Flow)

# ampFull$logArea <- log10(ampFull$Area)
# ampFull$logFlow <- log10(ampFull$Flow)

p1 <- multi_dotplot(amp, order, Area)
p2 <- multi_dotplot(amp, order, logArea)
p3 <- multi_dotplot(amp, order, Flow)
p4 <- multi_dotplot(amp, order, logFlow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, nrow = 2)

# Log transformation gives best distribution of these covariates

##############################################

# 2. Standardize variables for computational deficiency
amp$Year.std    <- (amp$Year-mean(amp$Year))/sd(amp$Year)
amp$logFlow.std <- (amp$logFlow-mean(amp$logFlow))/sd(amp$logFlow)
amp$logArea.std <- (amp$logArea-mean(amp$logArea))/sd(amp$logArea)
amp$aDepth.std  <- (amp$Depth_ave-mean(amp$Depth_ave))/sd(amp$Depth_ave)
amp$mDepth.std  <- (amp$Depth_max-mean(amp$Depth_max))/sd(amp$Depth_max)

# ampFull$Year.std    <- (ampFull$Year-mean(ampFull$Year))/sd(ampFull$Year)
# ampFull$logFlow.std <- (ampFull$logFlow-mean(ampFull$logFlow))/sd(ampFull$logFlow)
# ampFull$logArea.std <- (ampFull$logArea-mean(ampFull$logArea))/sd(ampFull$logArea)
# ampFull$aDepth.std  <- (ampFull$Depth_ave-mean(ampFull$Depth_ave))/sd(ampFull$Depth_ave)
# ampFull$mDepth.std  <- (ampFull$Depth_max-mean(ampFull$Depth_max))/sd(ampFull$Depth_max)
dim(amp)
dim(ampFull)

#create a dataset with three lakes excluded (those sampled with a handnet)
ampTest <- amp %>% filter (!Lake_abbr %in% three_lakes)
dim(ampTest)
length(unique(amp$Lake_code))
length(unique(ampTest$Lake_code))

```

## Find an optimal model

```{r}

#ull model
AM1 <- glmmTMB(Rel_amp ~ Period + logFlow.std + logArea.std + aDepth.std + PC +
                          (1|fLake),
                          compois(link = "log"),
                          data = amp)

drop1(AM1)

#             Df    AIC
# <none>         188.51
# Period       1 188.79
# logFlow.std  1 191.16
# logArea.std  1 186.54 <- drop
# aDepth.std   1 203.28
# PC           1 186.68 <- this one is also very close in terms of their AIC value
## repeated with full data and strict period 
#             Df    AIC
# <none>         213.94
# Period       1 218.18
# logFlow.std  1 220.19
# logArea.std  1 212.71
# aDepth.std   1 240.54
# PC           1 211.97 <- drop


#or do the same but with the maximum depth 
AM1max <- glmmTMB(Rel_amp ~ Period + logFlow.std + logArea.std + mDepth.std + PC +
                          (1|fLake),
                          compois(link = "log"),
                          data = amp)

drop1(AM1max)
#             Df    AIC
# <none>         192.03
# Period       1 193.15
# logFlow.std  1 194.25
# logArea.std  1 190.26 <- this one is also very close in terms of their AIC value
# mDepth.std   1 203.28
# PC           1 190.18 <- drop
## repeated with full data and strict period
#             Df    AIC
# <none>         218.68
# Period       1 224.29
# logFlow.std  1 223.85
# logArea.std  1 216.69 <- drop
# mDepth.std   1 240.54
# PC           1 217.24


#results with max and average depths are very similar, but average depths gives lower AIC values so we go with them. The average depth model suggested we drop lake are first. When comparing with the full dataset and strict division into two periods, we also get very similar results - dropping area or PC first. 

AM1a <- glmmTMB(Rel_amp ~ Period + logFlow.std + PC + aDepth.std +
                 (1|fLake),
               compois(link = "log"),
               data = amp)

drop1(AM1a)
#             Df    AIC
# <none>         186.54
# Period       1 186.93
# logFlow.std  1 190.04
# PC           1 184.68 <- drop
# aDepth.std   1 202.11
## repeated with full data and strict period
#             Df    AIC
# <none>         212.71
# Period       1 216.83
# logFlow.std  1 218.21
# PC           1 210.71  <- drop
# aDepth.std   1 238.57

AM1b <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std +
                  (1|fLake),
                compois(link = "log"),
                data = amp)

drop1(AM1b)
#             Df    AIC
# <none>         184.68 <- cannot improve fit by dropping further variables as this value is lowest
# Period       1 186.81
# logFlow.std  1 188.04
# aDepth.std   1 200.11
## repeated with full data and strict period
#             Df    AIC
# <none>         210.71 <- cannot improve fit by dropping further variables as this value is lowest
# Period       1 216.70
# logFlow.std  1 216.31
# aDepth.std   1 236.94

# Improve fit with different link function?
AM1c <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std +
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)

AIC(AM1b, AM1c)
#      df      AIC
# AM1b  6 184.6772
# AM1c  6 179.8158 <- better fit
## repeated with full data and strict period
#      df      AIC
# AM1b  6 210.7110
# AM1c  6 205.8885 <- better fit

# The optimal model is
AM2 <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std + 
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)
summary(AM2)
# just add the PC crustaceans
AM2_pc <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std + PC +
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)
AIC(AM2, AM2_pc)
#comparing with and without PC crustaceans
#        df      AIC
# AM2     6 205.8885
# AM2_pc  7 294.5522

```

## Sensitivity analyses: three lakes removed

```{r}
## repeat same analyses with three lakes dropped 

AM1_t <- glmmTMB(Rel_amp ~ Period + logFlow.std + logArea.std + aDepth.std + PC +
                          (1|fLake),
                          compois(link = "log"),
                          data = ampTest)

drop1(AM1_t)

#this was original data without three lakes dropped (not the full dataset)
#             Df    AIC
# <none>         188.51
# Period       1 188.79
# logFlow.std  1 191.16
# logArea.std  1 186.54 <- drop
# aDepth.std   1 203.28
# PC           1 186.68 <- this one is also very close in terms of their AIC value
#this is the model with three lakes removed
#             Df    AIC
# <none>         177.90
# Period       1 177.62
# logFlow.std  1 179.78
# logArea.std  1 175.91 <- drop
# aDepth.std   1 191.78
# PC           1 176.32 <- this one is also very close in terms of their AIC value

AM1a_t <- glmmTMB(Rel_amp ~ Period + logFlow.std + PC + aDepth.std +
                 (1|fLake),
               compois(link = "log"),
               data = ampTest)

drop1(AM1a_t)
#original
#             Df    AIC
# <none>         186.54
# Period       1 186.93
# logFlow.std  1 190.04
# PC           1 184.68 <- drop
# aDepth.std   1 202.11
#without three lakes
#             Df    AIC
# <none>         175.91
# Period       1 175.69
# logFlow.std  1 178.54
# PC           1 174.33 <- drop
# aDepth.std   1 190.61

AM1b_t <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std +
                  (1|fLake),
                compois(link = "log"),
                data = ampTest)

drop1(AM1b_t)
#original
#             Df    AIC
# <none>         184.68 <- cannot improve fit by dropping further variables as this value is lowest
# Period       1 186.81
# logFlow.std  1 188.04
# aDepth.std   1 200.11
#three lakes removed 
#             Df    AIC
# <none>         174.33 <- cannot improve fit by dropping further variables as this value is lowest
# Period       1 176.04
# logFlow.std  1 176.62
# aDepth.std   1 188.67

# Improve fit with different link function?
AM1c_t <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std +
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = ampTest)

AIC(AM1b_t, AM1c_t)
#        df      AIC
# AM1b_t  6 174.3343
# AM1c_t  6 169.5850 <- better fit

# The optimal model is
AM2 <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std + 
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)



```

## Model exploration 

```{r}
# Plot the residuals vs fitted values.
par(mfrow = c(1,1), mar = c(5,5,2,2))
E1 <- resid(AM2, type = "pearson")
F1 <- fitted(AM2)
plot(x = F1, 
     y = E1,
     xlab = "Fitted values",
     ylab = "Pearson residuals",
     pch = 16, cex.lab = 1.5)
abline(0, 0, lty = 2)
# OK

# Plot the residuals vs parameters in the model
par(mfrow = c(1,3), mar = c(5,5,2,2))

#Flow
plot(x = amp$logFlow.std, 
     y = E1,
     xlab = "Standardised flow",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

#Average depth
plot(x = amp$aDepth.std, 
     y = E1,
     xlab = "Average depth",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

#Period
boxplot(E1 ~ Period, data = amp,
        xlab = "Period",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Variables not in the model
par(mfrow = c(1,2), mar = c(5,5,2,2))

# Plot the residuals vs area
plot(x = amp$logArea.std, 
     y = E1,
     xlab = "Standardised log area",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# OK

#PC
boxplot(E1 ~ PC, data = amp,
        xlab = "PC",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Assess spatial dependency
# Sample-variogram
mydata <- data.frame(E1, amp$Lat, amp$Lon)
coordinates(mydata) <- c("amp.Lat", "amp.Lon")
V1 <- variogram(E1 ~ 1, mydata, cutoff = 2)
plot(V1, pch = 16, col = 1, cex = 1.5,
     xlab = list(label = "Distance", cex = 1.5),
     ylab = list(label = "Semi-variance", cex = 1.5) )
# No strong spatial trend

```

## Plot model 

```{r}
# Plot fixed effects
set_theme(
  base = theme_bw(),
  axis.textsize = 1)
plot_model(AM2, vline.color = "red", 
           sort.est = FALSE, 
           show.values = TRUE)
# Good

# Random effects
plot_model(AM2, vline.color = "green", type = "re")
# OK

# Model predictions
set_theme(
  axis.ticksize.x = 0.5,
  axis.ticksize.y = 0.5,
  axis.textsize.x = 0.5,
  axis.textsize.y = 0.5,
  axis.linecolor = "black", 
  axis.textcolor = "black",
  axis.tickslen = 0,
  axis.title.size = 0.9,
  axis.title.color = "black",
  axis.textsize = 0.9,
  geom.outline.size = 1,
  legend.pos = "bottom",
  legend.title.face = "italic",
  legend.backgroundcol = "white",
  legend.item.backcol = "white",
  legend.item.bordercol = "white",
  base = theme_blank())

# Define preferred figure format
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))

# The optimal model was
AM2 <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std +
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)
plot1 <- plot_model(AM2,
                    type = "pred", 
                    terms = c("logFlow.std", "Period"),
                    colors = c("blue", "firebrick2"),
                    show.data = T,
                    pred.type = c("fe"),
                    scale_y_continuous(limits = c(1,3)),
                    title = "",
                    show.legend = F,
                    jitter = 0.1,
                    axis.title = c("Mean standardized Log10 annual water renewal rate",
                                   "Categorical abundance of relict amphipods"),
                    show.values = F) + My_theme +
  scale_y_continuous(limits = c(-0.5, 5), breaks = c(0, 1, 2, 3))

# average depth
plot2 <- plot_model(AM2,
                    type = "pred", 
                    terms = c("aDepth.std", "Period"),
                    colors = c("blue", "firebrick2"),
                    show.data = T,
                    pred.type = c("fe"),
                    scale_y_continuous(limits = c(1,3)),
                    title = "",
                    show.legend = F,
                    jitter = 0.1,
                    axis.title = c("Mean standardized average lake depth",
                                   ""),
                    show.values = F) + My_theme +
  scale_y_continuous(limits = c(-0.5, 5), breaks = c(0, 1, 2, 3)) 
  #scale_x_continuous(limits = c(5, 20), breaks = c(5,10,15,20)) 


# # # Run model without standardised variables for a more intuitive plot
# AM2 <- glmmTMB(Rel_amp ~ Period + logFlow + Depth_ave +
#                         (1|fLake),
#                         compois(link = "sqrt"),
#                         data = amp)
# # # log flow
# plot1 <- plot_model(AM2,
#                     type = "pred",
#                     terms = c("logFlow [all]", "Period"),
#                     colors = c("blue", "firebrick2"),
#                     show.data = T,
#                     pred.type = c("fe"),
#                     scale_y_continuous(limits = c(1,3)),
#                     title = "",
#                     show.legend = F,
#                     jitter = 0.1,
#                     axis.title = c("Log10 annual water renewal rate",
#                                    "Categorical abundance of relict amphipods"),
#                     show.values = F) + My_theme +
#   scale_y_continuous(limits = c(-2, 7), breaks = c(0, 1, 2, 3))
# 
# # average depth
# plot2 <- plot_model(AM2,
#                     type = "pred", 
#                     terms = c("Depth_ave [all]", "Period"),
#                     colors = c("blue", "firebrick2"),
#                     show.data = T,
#                     pred.type = c("fe"),
#                     scale_y_continuous(limits = c(1,3)),
#                     title = "",
#                     show.legend = F,
#                     jitter = 0.1,
#                     axis.title = c("Average lake depth (m)",
#                                    ""),
#                     show.values = F) + My_theme +
#   scale_y_continuous(limits = c(-0.5, 5), breaks = c(0, 1, 2, 3)) +
#   scale_x_continuous(limits = c(5, 20), breaks = c(5,10,15,20)) 

grid.arrange(plot1, plot2, nrow = 1)

#Make a table for model summary
tab_model(AM2,
          show.zeroinf = F,
          dv.labels = c("Conway-Maxwell Poisson GLMM (relic amphipod)"),
          string.pred = "Coefficient",
          string.ci = "Conf. Int (95%)",
          string.p = "P-value",
          p.style = c("numeric"),
          emph.p = FALSE,
          transform = NULL,
          file = "amphipod_model.doc")

```
