---
    title: "Analysis of Mysis relicta occurrence in Lithuania"
author: "Carl Smith, Asta Audzijonyte, Kestutis Arbaciauskas"
date: "2022-09-06"
output: html_document
---

## Libraries
    
```{r message=FALSE}
library(tidyverse)
library(lattice)
library(sp)
library(gstat)
library(ggplot2)
library(fields)
library(dplyr)
library(tidyr)
library(performance)
library(see)
library(devtools)
library(outliers)
library(car)
library(effects)
library(lme4)
library(nlme)
library(glmmTMB)
library(lmerTest)
library(MuMIn)
library(performance)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(gridExtra)
library(GGally)
library(plyr)
library(DHARMa)
```

## Read in the data

```{r}
# Import dataframe
amp <- read_csv(file = "amp_clean.csv")
glimpse(amp)

# 'data.frame':	49 obs. of  16 variables:
```

## Data exploration

```{r}
#Any NAs
colSums(is.na(amp))
# No

# OUTLIERS

# Define preferred figure format
My_theme <- theme(axis.text.y = element_blank(),
                  axis.ticks.y = element_blank(),
                  axis.ticks.x = element_blank(),
                  panel.background = element_blank(),
           panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                 color = "white", size = 1),
                              text = element_text(size = 14),
                panel.grid.major = element_line(colour = "white", size = 0.1),
                panel.grid.minor = element_line(colour = "white", size = 0.1))

# A function for dotplots
multi_dotplot <- function(filename, Xvar, Yvar){
  filename %>%
    ggplot(aes(x = {{Xvar}})) +
    geom_point(aes(y = {{Yvar}})) +
    theme_bw() +
    coord_flip() +
    labs(x = "Order of Data")}

#Add ordered observations
amp <- amp %>%
  mutate(order = seq(1:nrow(amp)))

#Select continuous variables to plot
p1 <- multi_dotplot(amp, order, Year)
p2 <- multi_dotplot(amp, order, Rel_amp)
p3 <- multi_dotplot(amp, order, Rel_amp)
p4 <- multi_dotplot(amp, order, PC_amp)
p5 <- multi_dotplot(amp, order, PC_amp)
p6 <- multi_dotplot(amp, order, Area)
p7 <- multi_dotplot(amp, order, Depth_max)
p8 <- multi_dotplot(amp, order, Depth_ave)
p9 <- multi_dotplot(amp, order, Flow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3)

# 1. PC_amp and PC_amp have a lot of zeros
# 2. Area and flow with serious outliers
# 3. Rel_amp could have a problem with zero inflation

# Are data balanced among levels of the categorical covariates?

amp$fLake <- as.factor(amp$Lake_abbr)
table(amp$fLake)
# OK

table(amp$Year)
# Not great

table(amp$Period)
# Good

table(amp$B_amp)
# 0  1 
# 8 41

table(amp$Rel_amp)
# 0  1  2  3 
# 8  8  6 27 

table(amp$PC)
# OK

######################################
#NUMBER OF ZEROS IN THE RESPONSE VARIABLES

# What is the percentage of zeros for response variables?

sum(amp$Rel_amp == 0)
# 7 zeros

######################################

#NORMALITY AND HOMOGENEITY OF DEPENDENT VARIABLE(S)

# Frequency polygon plot - Rel_amp
amp %>% ggplot(aes(Rel_amp)) +
  geom_freqpoly( bins = 3) +
  labs(x = "Relic ampid abundance", y = "Frequency") +
  My_theme +
  theme(panel.border = element_rect(colour = "black", 
                                    fill=NA, size = 1))


#COLLINEARITY
# a summary using the ggpairs command from the GGally library
amp %>% 
  ggpairs(columns = c("Year", "PC_amp", "PC_amp", "PC",
                      "Area", "Depth_max", "Depth_ave", "Flow"), 
          aes(alpha = 0.8), lower = list(combo = wrap("facethist", binwidth = 2))) + 
  My_theme

# PC_amp and PC_amp correlated (use PC instead)
# Average and max depth correlated (use one or the other)

#####################################

#PLOT RELATIONSHIPS

# Plot response variable against covariates
par(mfrow=c(2,3), mar=c(5,5,1,1), cex.lab = 1)
plot(Rel_amp ~ Area,  data = amp,
     xlab = "Area",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Flow,  data = amp,
     xlab = "Flow",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Depth_max,  data = amp,
     xlab = "Max depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Depth_ave,  data = amp,
     xlab = "Ave depth",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

plot(Rel_amp ~ Year,  data = amp,
     xlab = "Year",
     ylab = "Rel_amp",
     pch = 16, cex = 1.3)

# Any evidence of interactions
ggplot(amp, aes(x = Flow, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Depth_ave, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Depth_max, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)


ggplot(amp, aes(x = Area, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

ggplot(amp, aes(x = Year, y = Rel_amp)) +
  geom_point(colour = 'gray44') +
  geom_smooth(method = 'lm', colour = 'black', se = FALSE) +
  theme(panel.background = element_blank()) +
  theme(panel.border = element_rect(fill = NA, size = 1)) +
  theme(strip.background = element_rect(fill = "white", 
                                        color = "white", size = 1)) +
  theme(text = element_text(size=16)) +
  facet_wrap(~PC)

# Temporal pattern?
ggplot() +
  geom_point(data = amp, 
                    aes(y = Rel_amp, x = Year),
                    shape = 16, 
                    size = 2)# +
  # facet_wrap( ~ Lake_abbr, scales = "fixed")

# Check temporal autocorrelation with ACF plot
B0 <- gls(B_amp ~ Year, 
          data = amp,
          na.action = na.omit,
          method = "REML")

par(mfrow = c(1,1), 
    cex.lab = 1.5, 
    mar = c(5,5,2,2), 
    cex.main = 1.5)

E0Full <- rep(NA, nrow(amp))
I      <- is.na(amp$Year) | is.na(amp$B_amp)
E0     <- resid(B0, type = "n")
E0Full[!I] <- E0

acf(E0Full, na.action = na.pass)
# No evidence of autocorrelation based on ACF plot

```
### What variables predict presence/abundance of relic amphipods?

 Data exploration shows:

 -Outliers in Area and Flow
 -Zeros in the response variable
 -Imbalance in Ponto-Caspian ampacean abundance
 -Collinearity with average and maximum depth, PC amp and amp
 -No obviously strong interactions
 -Same sites sampled on multiple occasions (dependency)

Next steps:

 1. log transform flow and area
 2. Standardize variables for computational efficiency
 3. fit GLMM (lake as random intercept)
 4. model presence/absence with Bernoulli distribution

### Log transorm and standardise data

```{r}

# 1. log transform flow and area to improve distribution
amp$logArea <- log10(amp$Area)
amp$logFlow <- log10(amp$Flow)

p1 <- multi_dotplot(amp, order, Area)
p2 <- multi_dotplot(amp, order, logArea)
p3 <- multi_dotplot(amp, order, Flow)
p4 <- multi_dotplot(amp, order, logFlow)

#Plot as a grid
grid.arrange(p1, p2, p3, p4, nrow = 2)

# Log transformation gives best distribution of these covariates

##############################################

# 2. Standardize variables for computational efficieny
amp$Year.std    <- (amp$Year-mean(amp$Year))/sd(amp$Year)
amp$logFlow.std <- (amp$logFlow-mean(amp$logFlow))/sd(amp$logFlow)
amp$logArea.std <- (amp$logArea-mean(amp$logArea))/sd(amp$logArea)
amp$aDepth.std  <- (amp$Depth_ave-mean(amp$Depth_ave))/sd(amp$Depth_ave)
amp$mDepth.std  <- (amp$Depth_max-mean(amp$Depth_max))/sd(amp$Depth_max)

```

## Fit a model and explore 

```{r}

CMP1 <- glmmTMB(Rel_amp ~ Period + logFlow.std + logArea.std + aDepth.std + PC +
                          (1|fLake),
                          compois(link = "sqrt"),
                          data = amp)
summary(CMP1)
#      AIC      BIC   logLik deviance df.resid 
#    331.3    351.3   -157.6    315.3       82 
# 
# Random effects:
# 
# Conditional model:
#  Groups Name        Variance Std.Dev.
#  fLake  (Intercept) 0.6697   0.8184  
# Number of obs: 90, groups:  fLake, 45
# 
# Dispersion parameter for compois family (): 0.226 
# 
# Conditional model:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.96357    0.13813   6.976 3.04e-12 ***
# PeriodP2    -0.10196    0.08427  -1.210    0.226    
# logFlow.std  0.09542    0.14529   0.657    0.511    
# logArea.std -0.14004    0.13321  -1.051    0.293    
# aDepth.std  -0.06046    0.13650  -0.443    0.658    
# PCpresent   -0.02737    0.13126  -0.209    0.835    

drop1(CMP1)

# Single term deletions
# Model:
# Rel_amp ~ Period + logFlow.std + logArea.std + aDepth.std + PC + 
#     (1 | fLake)
#             Df    AIC
# <none>         331.29
# Period       1 259.09
# logFlow.std  1 329.43
# logArea.std  1 312.83
# aDepth.std   1 439.86
# PC           1 248.11

# The optimal model is
CMP2 <- glmmTMB(Rel_amp ~ Period + logFlow.std + aDepth.std + 
                          (1|fLake),
                           compois(link = "sqrt"),
                           data = amp)

summary(CMP2)

#      AIC      BIC   logLik deviance df.resid 
#      212      227     -100      200       84 
# 
# Random effects:
# 
# Conditional model:
#  Groups Name        Variance Std.Dev.
#  fLake  (Intercept) 0.02031  0.1425  
# Number of obs: 90, groups:  fLake, 45
# 
# Dispersion parameter for compois family (): 0.193 
# 
# Conditional model:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  1.39898    0.04431  31.576  < 2e-16 ***
# PeriodP2    -0.13480    0.05835  -2.310  0.02087 *  
# logFlow.std  0.11023    0.03642   3.027  0.00247 ** 
# aDepth.std   0.24434    0.03799   6.432 1.26e-10 ***


# Plot the residuals vs fitted values.
par(mfrow = c(1,1), mar = c(5,5,2,2))
E1 <- resid(CMP2, type = "pearson")
F1 <- fitted(CMP2)
plot(x = F1, 
     y = E1,
     xlab = "Fitted values",
     ylab = "Pearson residuals",
     pch = 16, cex.lab = 1.5)
abline(0, 0, lty = 2)
# OK

# Plot the residuals vs parameters in the model
par(mfrow = c(1,3), mar = c(5,5,2,2))

#Flow
plot(x = amp$logFlow.std, 
     y = E1,
     xlab = "Standardised flow",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

#Average depth
plot(x = amp$aDepth.std, 
     y = E1,
     xlab = "Average depth",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

#Period
boxplot(E1 ~ Period, data = amp,
        xlab = "Period",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Variables not in the model
par(mfrow = c(1,3), mar = c(5,5,2,2))

# Plot the residuals vs ave depth
plot(x = amp$mDepth.std, 
     y = E1,
     xlab = "Standardised max depth",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)

# Plot the residuals vs area
plot(x = amp$logArea.std, 
     y = E1,
     xlab = "Standardised log area",
     ylab = "Pearson residuals", 
     pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# OK

#Period
boxplot(E1 ~ PC, data = amp,
        xlab = "PC",
        ylab = "",
        range=0,
        pch = 16, cex.lab = 1.5)
abline(0,0, lty=2)
# They are fine

# Assess spatial dependency
# Sample-variogram
mydata <- data.frame(E1, amp$Lat, amp$Lon)
coordinates(mydata) <- c("amp.Lat", "amp.Lon")
V1 <- variogram(E1 ~ 1, mydata, cutoff = 2)
plot(V1, pch = 16, col = 1, cex = 1.5,
     xlab = list(label = "Distance", cex = 1.5),
     ylab = list(label = "Semi-variance", cex = 1.5) )
# No obvious spatial trend

```

### Plot model 

```{r}
# Plot fixed effects
set_theme(
  base = theme_bw(),
  axis.textsize = 1)
plot_model(CMP2, vline.color = "red", 
           sort.est = FALSE, 
           show.values = TRUE)
# Good

# Random effects
plot_model(CMP2, vline.color = "green", type = "re")
# Quite limited lake effects

# Model predictions
set_theme(
  axis.ticksize.x = 0.5,
  axis.ticksize.y = 0.5,
  axis.textsize.x = 0.5,
  axis.textsize.y = 0.5,
  axis.linecolor = "black", 
  axis.textcolor = "black",
  axis.tickslen = 0.2,
  axis.title.size = 0.9,
  axis.title.color = "black",
  axis.textsize = 0.8,
  geom.outline.size = 1,
  legend.pos = "bottom",
  legend.title.face = "italic",
  legend.backgroundcol = "white",
  legend.item.backcol = "white",
  legend.item.bordercol = "white",
  base = theme_blank())

# Define preferred figure format
My_theme <- theme(panel.background = element_blank(),
                  panel.border = element_rect(fill = NA, size = 1),
                  strip.background = element_rect(fill = "white", 
                                                  color = "white", size = 1),
                  text = element_text(size = 14),
                  panel.grid.major = element_line(colour = "white", size = 0.1),
                  panel.grid.minor = element_line(colour = "white", size = 0.1))


# Plot model

# log flow
plot2 <- plot_model(CMP2,
                    type = "pred", 
                    terms = c("logFlow.std [all]", "Period"),
                    colors = c("blue", "firebrick2", "green2"),
                    show.data = T,
                    pred.type = c("fe"),
                    title = "",
                    show.legend = TRUE,
                    jitter = 0.5,
                    axis.title = c("Log flowthrough (standardised)",
                                   "Relative abundance of glacial relict amphipods"),
                    show.values = F) + My_theme
# average depth
plot3 <- plot_model(CMP2,
                    type = "pred", 
                    terms = c("aDepth.std [all]", "Period"),
                    colors = c("blue", "firebrick2", "green2"),
                    show.data = T,
                    pred.type = c("fe"),
                    title = "",
                    show.legend = TRUE,
                    jitter = 0.5,
                    axis.title = c("Average depth (standardised)",
                                   ""),
                    show.values = F) + My_theme

grid.arrange(plot2, plot3, nrow = 1)

# Model summary
summary(CMP2)

#              Estimate Std. Error z value Pr(>|z|)    
#(Intercept)   1.39898    0.04431  31.576  < 2e-16 ***
# PeriodP2    -0.13480    0.05835  -2.310  0.02087 *  
# logFlow.std  0.11023    0.03642   3.027  0.00247 ** 
# aDepth.std   0.24434    0.03799   6.432 1.26e-10 ***

tab_model(CMP2,
          show.zeroinf = F,
          dv.labels = c("Conway-Maxwell Poisson GLMM (relic amphipods)"),
          string.pred = "Coefficient",
          string.ci = "Conf. Int (95%)",
          string.p = "P-value",
          p.style = c("numeric"),
          emph.p = FALSE,
          transform = NULL,
          file = "amp.doc")

```
